Manuscript plots

### 2023-12-15 manuscript_modelling_and_plots.Rmd
adding a small note on whether estimates are marginal and conditional - marginal seems to be the default.
some description on what the model is actually doing

*add_epred_draws()* adds draws from the expectation of the posterior predictive distribution. Provides the expected means from the model.

@@

>>>>

*add_epred_draws()* adds draws from the expectation of the posterior predictive distribution. Provides the expected means from the model. The default for the re_formula is NULL which includes the groups level effects which thus produces marginal effects (incorportates the random effects in the estimate).

@@

This basically calculating the conditional effects for the existing groups in the dataset. This tutorial (https://www.andrewheiss.com/blog/2021/11/10/ame-bayes-re-guide/#conditional-effects-for-existing-groups) produces the same values - I just use parameters straight from the model to calculate the individual effects. Using that tutorial also provides 95% HDIs for each individual.
